Let's talk about Thurstone & Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-06-02 paper2.qmd
section:6; process:write

<!-- 5. Are there any additional advantages? -->
Beyond these potential benefits, the approach offers two additional advantages. First, it clarifies the roles and interactions of all actors and processes involved in CJ experiments. Second, it shifts the analytic paradigm from passively accepting the assumptions of the BTL model to actively testing their fit with observed data. Together, these advantages establish a principled framework for evaluating best practices in CJ experimental designs, one that better aligns with the demands of contemporary CJ assessment contexts [@Kelly_et_al_2022], offering new insights into existing research and opening promising avenues for future inquiry. Five current and new research avenues deserve particular attention due to their direct impact on the reliability and validity of trait estimates and the accuracy of statistical inferences. The following sections outline these avenues and explain how our model provides a rigorous research framework to investigate them.

@@

## The impact of sampling and comparison mechanisms on CJ outcomes and inference robustness {#sec-discussion_RA1}
<!-- recording: Sven and Tine 25.05.21; time: 00:03:30 - 00:24:00 -->

@@

## The effects of judges' bias on the reliability of traits {#sec-discussion_RA2}
<!-- recording: Sven and Tine 25.05.21; time: 00:24:00 - 00:31:45 -->

@@

## The identification of 'misfitting' judges and stimuli {#sec-discussion_RA3}
<!-- recording: Sven and Tine 25.05.21; time: 00:31:45 - 00:32:20 -->

@@

## The effects of hierarchies on experimental design and inference {#sec-discussion_RA4}
<!-- recording: Sven and Tine 25.05.21; time: 00:32:25 - 00:33:00 -->

@@

## The effects of non-dichotomous outcomes and multidimensional traits on CJ experiments {#sec-discussion_RA5}

>>>>

<!-- 5. Are there any additional advantages? -->
Beyond these potential benefits, the approach offers two additional advantages. First, it clarifies the roles and interactions of all actors and processes involved in CJ experiments. Second, it shifts the analytic paradigm from passively accepting the assumptions of the BTL model to actively testing their fit with observed data. Together, these advantages establish a principled framework for evaluating best practices in CJ experimental designs, one that better aligns with the demands of contemporary CJ assessment contexts [@Kelly_et_al_2022], offering new insights into existing research and opening promising avenues for future inquiry.

@@

## Future research {#sec-discussion_RA}

Five current and new research avenues deserve particular attention due to their direct impact on the reliability and validity of trait estimates and the accuracy of statistical inferences. The following sections outline these avenues and explain how our model provides a rigorous research framework to investigate them.

### The impact of sampling and comparison mechanisms {#sec-discussion_RA1}
<!-- recording: Sven and Tine 25.05.21; time: 00:03:30 - 00:24:00 -->

@@

### The effects of judges' bias on the reliability of traits {#sec-discussion_RA2}
<!-- recording: Sven and Tine 25.05.21; time: 00:24:00 - 00:31:45 -->

@@

### The identification of 'misfitting' judges and stimuli {#sec-discussion_RA3}
<!-- recording: Sven and Tine 25.05.21; time: 00:31:45 - 00:32:20 -->

@@

### The effects of hierarchies on experimental design and inference {#sec-discussion_RA4}
<!-- recording: Sven and Tine 25.05.21; time: 00:32:25 - 00:33:00 -->

@@

### The effects of non-dichotomous outcomes and multidimensional traits on CJ experiments {#sec-discussion_RA5}
